---
title: "Free Recall"
author: "Barry Sheppard"
date: "02 July 2016"
output: html_document
---

## Free Recall Results

```{r load, include=FALSE}
# Loading up some data
library(tidyr)
library(psych)
library(BayesFactor)
library(MASS)
library(vcd)

source("load.R", print.eval=TRUE)

# Rename for the graph
library(plyr)

# I'm being lazy and reusing the prompted_recall code as is
prompted_recall <- rename(f_recall, c("recall"="Recall", "product"="Product", "endorse"="Endorsement"))
# Table for prompted Recall
prompted_recall_table <- xtabs(~Product + Endorsement + Recall, data=prompted_recall)
```

## Analysis

### Responses

```{r, echo=FALSE}
# count the total responses per person (only valid responses)
print(c("Mean of responses", round(mean(free_recall[free_true,]$responses), 2)))
print(c("Standard deviation of responses", round(sd(free_recall[free_true,]$responses),2)))

# Count of correct data
print(c("Mean of correct responses", round(mean(free_recall[free_true,]$count),2)))
print(c("Standard deviation of correct responses", round(sd(free_recall[free_true,]$count),2)))
```

## 2x2 Breakdowns - Products

### Product: Healthy vs Unhealthy

```{r, echo=FALSE, error=FALSE}
# Subset the data to remove NonFood so we can compare Unhealthy and Healthy 
data_subset <- subset(prompted_recall, Product!="NonFood")
# Refactor Product to remove the unused factor
data_subset$Product <- factor(data_subset$Product)
# Prepare the data
prompted_recall_table_1 <- xtabs(~ Product + Recall, data_subset)
# Show the data
ftable(data_subset)

# Summarise the results
P1 <- summary(prompted_recall_table_1)
P1
print(c("P = ", format(P1$p.value, scientific=FALSE)))

# Bayes Factors - indepMultinomial, generalised form
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))

# This is a Log Linear model and displayed as a mosaic, a little excessive as we're only displaying the table
model_joint_indep <- loglm(formula = ~ Product + Recall, data=prompted_recall_table_1)
plot(model_joint_indep, panel = mosaic, type = "observed", pop=FALSE, shade=FALSE, legend=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)
```

### Product: Nonfood vs Unhealthy

```{r, echo=FALSE}

# Subset the data to remove NonFood so we can compare Unhealthy and Nonfood
data_subset <- subset(prompted_recall, Product!="Healthy")
# Refactor Product to remove the unused factor
data_subset$Product <- factor(data_subset$Product)
# Prepare the data
prompted_recall_table_1 <- xtabs(~Product + Recall, data_subset)
# Show the data
ftable(data_subset)
# Summarise results 
P1 <- summary(prompted_recall_table_1)
P1
print(c("P = ", format(P1$p.value, scientific=FALSE)))
# Bayes Factors
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))
# This is a Log Linear model and displayed as a mosaic, a little excessive as we're only displaying the table
model_joint_indep <- loglm(formula = ~ Product + Recall, data=prompted_recall_table_1)
plot(model_joint_indep, panel = mosaic, type = "observed", pop=FALSE, shade=FALSE, legend=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)
```

### Product: Healthy vs Nonfood

```{r, echo=FALSE}
# Subset the data to remove NonFood so we can compare Healthy and Nonfood
data_subset <- subset(prompted_recall, Product!="Unhealthy")
# Refactor Product to remove the unused factor
data_subset$Product <- factor(data_subset$Product)
# Prepare the data
prompted_recall_table_1 <- xtabs(~Product + Recall, data_subset)
# Show the data
ftable(data_subset)
# Summarise results 
P1 <- summary(prompted_recall_table_1)
P1
print(c("P = ", format(P1$p.value, scientific=FALSE)))
# Bayes Factors
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))
# This is a Log Linear model and displayed as a mosaic, a little excessive as we're only displaying the table
model_joint_indep <- loglm(formula = ~ Product + Recall, data=prompted_recall_table_1)
plot(model_joint_indep, panel = mosaic, type = "observed", pop=FALSE, shade=FALSE, legend=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)
```


## 2x2 Breakdowns - Endorsement

### Endorsement: Peer vs Celebrity

```{r, echo=FALSE}
# Subset the data to remove Sponsored so we can compare Peer and Celebrity 
data_subset <- subset(prompted_recall, Endorsement!="Sponsored")
# Refactor Endorsement to remove the unused factor
data_subset$Endorsement <- factor(data_subset$Endorsement)
# Prepare the data
prompted_recall_table_1 <- xtabs(~Endorsement + Recall, data_subset)
# Show the data
ftable(data_subset)
# Summarise results 
P1 <- summary(prompted_recall_table_1)
P1
print(c("P = ", format(P1$p.value, scientific=FALSE)))
# Bayes Factors
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))
# This is a Log Linear model and displayed as a mosaic, a little excessive as we're only displaying the table
model_joint_indep <- loglm(formula = ~ Endorsement + Recall, data=prompted_recall_table_1)
plot(model_joint_indep, panel = mosaic, type = "observed", pop=FALSE, shade=FALSE, legend=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)
```

### Endorsement: Peer vs Sponsored

```{r, echo=FALSE}

# Subset the data to remove Celebrity so we can compare Peer and Sponsored 
data_subset <- subset(prompted_recall, Endorsement!="Celebrity")
# Refactor Endorsement to remove the unused factor
data_subset$Endorsement <- factor(data_subset$Endorsement)
# Prepare the data
prompted_recall_table_1 <- xtabs(~Endorsement + Recall, data_subset)
# Show the data
ftable(data_subset)
# Summarise results 
P1 <- summary(prompted_recall_table_1)
P1
print(c("P = ", format(P1$p.value, scientific=FALSE)))
# Bayes Factors
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))
# This is a Log Linear model and displayed as a mosaic, a little excessive as we're only displaying the table
model_joint_indep <- loglm(formula = ~ Endorsement + Recall, data=prompted_recall_table_1)
plot(model_joint_indep, panel = mosaic, type = "observed", pop=FALSE, shade=FALSE, legend=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)
```

### Endorsement: Celebrity vs Sponsored

```{r, echo=FALSE}

# Subset the data to remove Peer so we can compare Celebrity and Sponsored
data_subset <- subset(prompted_recall, Endorsement!="Peer")
# Refactor Endorsement to remove the unused factor
data_subset$Endorsement <- factor(data_subset$Endorsement)
# Prepare the data
prompted_recall_table_1 <- xtabs(~Endorsement + Recall, data_subset)
# Show the data
ftable(data_subset)
# Summarise results 
P1 <- summary(prompted_recall_table_1)
P1
print(c("P = ", format(P1$p.value, scientific=FALSE)))
# Bayes Factors
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))
# This is a Log Linear model and displayed as a mosaic, a little excessive as we're only displaying the table
model_joint_indep <- loglm(formula = ~ Endorsement + Recall, data=prompted_recall_table_1)
plot(model_joint_indep, panel = mosaic, type = "observed", pop=FALSE, shade=FALSE, legend=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)
```


## Analysis

Full interaction of Product * endorsement * Recall

```{r describe, echo=FALSE, messages=FALSE, warning=FALSE}

# Table the prompted Recall table
ftable(prompted_recall_table)
table <- ftable(prompted_recall_table)
print("Percentages")
round(prop.table(table, 1),2)

# Xtabs for the prompoted Recall
P1 <- summary(prompted_recall_table)
P1
print(c("P = ", format(P1$p.value, scientific=FALSE)))

BF1 <- contingencyTableBF(prompted_recall_table, sampleType = "indepMulti", fixedMargin = "rows")
BF1
print(c("BF10:", format(exp(BF1@bayesFactor$bf), scientific=FALSE)))

```



# The Log Linear Analysis

## First a mutual indepedence model with a plot to visualise the data

```{r}
# Mutual Independence: A, B, and C are pairwise independent.
model_mut_indep <- loglm(formula = ~ Endorsement + Product + Recall, data=prompted_recall_table)
plot(model_mut_indep, panel = mosaic, type = "observed", residuals_type = "pearson", gp = shading_hcl, gp_args = list(), pop=FALSE, shade=TRUE, legend=TRUE)
labeling_cells(text = prompted_recall_table, margin = 0)(prompted_recall_table)
summary(model_mut_indep)
```

## Saturated model : This generates a model based on the data, so residuals are 0

```{r}
model_log_sat <- loglm(~ Endorsement * Product * Recall, data=prompted_recall_table)
summary(model_log_sat)
```

## Without the 4/3 way interaction, this model takes away the combined interaction

```{r}
model_log_reduced <- loglm(~ Endorsement * Product * Recall - Endorsement:Product:Recall, data=prompted_recall_table)
plot(model_log_reduced, panel = mosaic, type = "observed", residuals_type = "pearson", gp = shading_hcl, gp_args = list(), pop=FALSE, shade=TRUE, legend=TRUE)
labeling_cells(text = prompted_recall_table, margin = 0)(prompted_recall_table)
model_log_reduced
```

## Removing the Endorsement interactions : This shows where product is having the biggest impact

```{r}
model_log_product <- loglm(~ Endorsement * Product * Recall - Endorsement:Product:Recall - Endorsement:Recall - Product:Endorsement, data=prompted_recall_table)
plot(model_log_product, panel = mosaic, type = "observed", residuals_type = "pearson", gp = shading_hcl, gp_args = list(), pop=FALSE, shade=TRUE, legend=TRUE)
labeling_cells(text = prompted_recall_table, margin = 0)(prompted_recall_table)
model_log_product
```

## Removing the Product interactions : This shows where endorsement is having the biggest impact

```{r}
model_log_endorse <- loglm(~ Endorsement * Product * Recall - Endorsement:Product:Recall - Product:Recall, data=prompted_recall_table)
plot(model_log_endorse, panel = mosaic, type = "observed", residuals_type = "pearson", gp = shading_hcl, gp_args = list(), pop=FALSE, shade=TRUE, legend=TRUE)
labeling_cells(text = prompted_recall_table, margin = 0)(prompted_recall_table)
```

## How different are the models?

```{r}
anova(model_log_sat, model_log_reduced, model_mut_indep, model_log_product, model_log_endorse, test = "Chisq")
```


Endorsement * Product
This should appear as a symmetrical 3 x 3 square as there are an equal number of all combinations

```{r, echo=FALSE}
# Endorsement * Product
T1 <- margin.table(prompted_recall_table, c(1,2)) 
T1
summary(T1)
mosaic(T1, shade=TRUE, legend=FALSE, pop=FALSE)
labeling_cells(text = T1, margin = 0)(T1)
```


Product * Recall

```{r, echo=FALSE}

# Product * Recall
T2 <- margin.table(prompted_recall_table, c(1,3)) 
T2
P2 <- summary(T2)
P2
print(c("P = ", format(P2$p.value, scientific=FALSE)))

BF2 <- contingencyTableBF(T2, sampleType = "indepMulti", fixedMargin = "rows")
BF2
print(c("BF10:", format(exp(BF2@bayesFactor$bf), scientific=FALSE)))

model <- loglm(formula = ~ Product + Recall, data=T2)
plot(model, panel = mosaic, type = "observed", pop=FALSE, shade=TRUE, legend=TRUE)
labeling_cells(text = T2, margin = 0)(T2)

```


Endorsement * Recall

```{r, echo=FALSE}
# Endorsement * Recall
T3 <- margin.table(prompted_recall_table, c(2,3)) 
T3
P3<- summary(T3)
P3
print(c("P = ", format(P3$p.value, scientific=FALSE)))

BF3 <- contingencyTableBF(T3, sampleType = "indepMulti", fixedMargin = "rows")
BF3
print(c("BF10:", format(exp(BF3@bayesFactor$bf), scientific=FALSE)))

model <- loglm(formula = ~ Endorsement + Recall, data=T3)
plot(model, panel = mosaic, type = "observed", pop=FALSE, shade=TRUE, legend=TRUE)
labeling_cells(text = T3, margin = 0)(T3)
```

