---
title: "Free Recall"
author: "Barry Sheppard"
date: "02 July 2016"
output: pdf_document
---

## Free Recall Results

```{r load, include=FALSE}
# Loading up some data
library(tidyr)
library(psych)
library(BayesFactor)
library(MASS)
library(vcd)

source("load.R", print.eval=TRUE)

# Rename for the graph
library(plyr)

# I'm being lazy and reusing the prompted_recall code as is
prompted_recall <- rename(f_recall, c("recall"="Recall", "product"="Product", "endorse"="Endorsement"))
# Table for prompted Recall
prompted_recall_table <- xtabs(~Product + Endorsement + Recall, data=prompted_recall)
```

## 2x2 Breakdowns - Products
Starting with the hypotheses for Product

```{r, echo=FALSE}

# Subset the data to remove NonFood so we can compare Unhealthy and Healthy 
data_subset <- subset(prompted_recall, Product!="NonFood")
# Refactor Product to remove the unused factor
data_subset$Product <- factor(data_subset$Product)
# Show the data
ftable(data_subset)
# Prepare the data
prompted_recall_table_1 <- xtabs(~Product + Recall, data_subset)
# Prepare the chart
mosaic(prompted_recall_table_1, shade=TRUE, legend=TRUE, pop=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)
# Summarise the results
P1 <- summary(prompted_recall_table_1)
P1
print(c("P = ", format(P1$p.value, scientific=FALSE)))
# Bayes Factors
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))

# Subset the data to remove NonFood so we can compare Unhealthy and Nonfood
data_subset <- subset(prompted_recall, Product!="Healthy")
# Refactor Product to remove the unused factor
data_subset$Product <- factor(data_subset$Product)
# Show the data
ftable(data_subset)
# Prepare the data
prompted_recall_table_1 <- xtabs(~Product + Recall, data_subset)
# Prepare the chart
mosaic(prompted_recall_table_1, shade=TRUE, legend=TRUE, pop=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)
# Summarise results 
P1 <- summary(prompted_recall_table_1)
P1
print(c("P = ", format(P1$p.value, scientific=FALSE)))
# Bayes Factors
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))

# Subset the data to remove NonFood so we can compare Healthy and Nonfood
data_subset <- subset(prompted_recall, Product!="Unhealthy")
# Refactor Product to remove the unused factor
data_subset$Product <- factor(data_subset$Product)
# Show the data
ftable(data_subset)
# Prepare the data
prompted_recall_table_1 <- xtabs(~Product + Recall, data_subset)
# Prepare the chart
mosaic(prompted_recall_table_1, shade=TRUE, legend=TRUE, pop=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)
# Summarise results 
P1 <- summary(prompted_recall_table_1)
P1
print(c("P = ", format(P1$p.value, scientific=FALSE)))
# Bayes Factors
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))

```


## 2x2 Breakdowns - Endorsement
Starting with the hypotheses for endorsement

```{r, echo=FALSE}
# Subset the data to remove Sponsored so we can compare Peer and Celebrity 
data_subset <- subset(prompted_recall, Endorsement!="Sponsored")
# Refactor Endorsement to remove the unused factor
data_subset$Endorsement <- factor(data_subset$Endorsement)
# Prepare the data
prompted_recall_table_1 <- xtabs(~Endorsement + Recall, data_subset)
# Show the data
ftable(data_subset)
# Prepare the chart
mosaic(prompted_recall_table_1, shade=TRUE, legend=TRUE, pop=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)
# Summarise results 
P1 <- summary(prompted_recall_table_1)
P1
print(c("P = ", format(P1$p.value, scientific=FALSE)))
# Bayes Factors
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))


# Subset the data to remove Celebrity so we can compare Peer and Sponsored 
data_subset <- subset(prompted_recall, Endorsement!="Celebrity")
# Refactor Endorsement to remove the unused factor
data_subset$Endorsement <- factor(data_subset$Endorsement)
# Prepare the data
prompted_recall_table_1 <- xtabs(~Endorsement + Recall, data_subset)
# Show the data
ftable(data_subset)
# Prepare the chart
mosaic(prompted_recall_table_1, shade=TRUE, legend=TRUE, pop=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)
# Summarise results 
P1 <- summary(prompted_recall_table_1)
P1
print(c("P = ", format(P1$p.value, scientific=FALSE)))
# Bayes Factors
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))



# Subset the data to remove Peer so we can compare Celebrity and Sponsored
data_subset <- subset(prompted_recall, Endorsement!="Peer")
# Refactor Endorsement to remove the unused factor
data_subset$Endorsement <- factor(data_subset$Endorsement)
# Prepare the data
prompted_recall_table_1 <- xtabs(~Endorsement + Recall, data_subset)
# Show the data
ftable(data_subset)
# Prepare the chart
mosaic(prompted_recall_table_1, shade=TRUE, legend=TRUE, pop=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)
# Summarise results 
P1 <- summary(prompted_recall_table_1)
P1
print(c("P = ", format(P1$p.value, scientific=FALSE)))
# Bayes Factors
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))

```


## Analysis

Full interaction of Product * endorsement * Recall

```{r describe, echo=FALSE, messages=FALSE, warning=FALSE}

# Table the prompted Recall table
ftable(prompted_recall_table)
# Xtabs for the prompoted Recall
P1 <- summary(prompted_recall_table)
P1
print(c("P = ", format(P1$p.value, scientific=FALSE)))

BF1 <- contingencyTableBF(prompted_recall_table, sampleType = "indepMulti", fixedMargin = "rows")
BF1
print(c("BF10:", format(exp(BF1@bayesFactor$bf), scientific=FALSE)))

mosaic(prompted_recall_table, shade=TRUE, legend=TRUE, pop=FALSE)
labeling_cells(text = prompted_recall_table, margin = 0)(prompted_recall_table)
```

Endorsement * Product
This should appear as a symmetrical 3 x 3 square as there are an equal number of all combinations

```{r, echo=FALSE}
# Endorsement * Product
T1 <- margin.table(prompted_recall_table, c(1,2)) 
T1
summary(T1)
mosaic(T1, shade=TRUE, legend=FALSE, pop=FALSE)
labeling_cells(text = T1, margin = 0)(T1)
```


Product * Recall

```{r, echo=FALSE}

# Product * Recall
T2 <- margin.table(prompted_recall_table, c(1,3)) 
T2
P2 <- summary(T2)
P2
print(c("P = ", format(P2$p.value, scientific=FALSE)))

BF2 <- contingencyTableBF(T2, sampleType = "indepMulti", fixedMargin = "rows")
BF2
print(c("BF10:", format(exp(BF2@bayesFactor$bf), scientific=FALSE)))

mosaic(T2, shade=TRUE, legend=TRUE, pop=FALSE)
labeling_cells(text = T2, margin = 0)(T2)

```


Endorsement * Recall

```{r, echo=FALSE}
# Endorsement * Recall
T3 <- margin.table(prompted_recall_table, c(2,3)) 
T3
P3<- summary(T3)
P3
print(c("P = ", format(P3$p.value, scientific=FALSE)))

BF3 <- contingencyTableBF(T3, sampleType = "indepMulti", fixedMargin = "rows")
BF3
print(c("BF10:", format(exp(BF3@bayesFactor$bf), scientific=FALSE)))

mosaic(T3, shade=TRUE, legend=TRUE, pop=FALSE)
labeling_cells(text = T3, margin = 0)(T3)
```

# The Log Linear Analysis

```{r}
summary(loglm(~ Endorsement + Product + Recall, data=prompted_recall_table))
```

Saturated model

```{r}
summary(loglm(~ Endorsement * Product * Recall, data=prompted_recall_table))
```

Without the 4/3 way interaction

```{r}
summary(loglm(~ Endorsement * Product * Recall - Endorsement:Product:Recall, data=prompted_recall_table))
```

