---
title: "Product Analysis"
author: "Barry Sheppard"
date: "21 June 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a breakdown of results based on products rather than factors. As there are a number of products which are only displayed to one gender, for totals these results were adjusted to give a proportional value (i.e. values were divided by total number of participants in that gender and multiplied by the total number of participants). Means are unadjusted.

```{r products, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

# Set working director
setwd("~/GitHub/KidsFoodandFacebook")

# Import Libraries required

# install.packages("magrittr")
library("magrittr")
# install.packages("tidyr")
library("tidyr")
# install.packages("ggplot2")
library("ggplot2")
# install.packages("cowplot")
library("cowplot")
# install.packages("plyr")
library("plyr")
# install.packages("psych)
library("psych")

library(ggthemes)

# Load the data
source("load.R", print.eval=TRUE)

# Familiarity totals

# Brand list
brands <- c("Ben & Jerries", "McDonalds", "Subway", "Luckies", "Tesco", "Good4U", "Bord Bia", "Jam", "Dior", "Sennheiser", "Eddie Rockets")
brands <- c(brands, "KFC", "Apache Pizza", "Uncle Bens Rice", "Danone", "Kelkin", "H&M", "Truly Kissable", "Adidas", "Doritos", "Coco pops")
brands <- c(brands, "Walkers", "Weetabix", "Fyffes", "Chopped", "Penneys", "Covergirl", "ASOS", "Bunsen", "Creme Egg", "Supermacs", "Special K")
brands <- c(brands, "John West", "The Foods of Athenry", "CB tanning", "Nike", "Under armor", "Uncharted 4", "Nerf", "Google", "Irish Pride")
brands <- c(brands, "Burger King", "Yoplait", "Keelings", "Avonmore", "Tayto", "Fruit & Fibre", "Reebok", "Domino's Pizza", "Hagen Daaz", "Ready Brek")
brands <- c(brands, "Dunnes", "Cheetos", "Kitkat", "Alpen Muesli", "Beats")

# Brand Type
brand.type.list <- c("UF", "UF", "UF", "NF", "HF", "HF", "HF", "NF", "NF", "NF", "UF", "UF", "UF", "HF", "HF", "HF", "NF", "NF", "NF", "UF", "UF", "UF", "HF", "HF", "HF", "NF", "NF", "NF", "UF", "UF", "UF", "HF", "HF", "HF", "NF", "NF", "NF", "NF", "NF", "NF", "HF", "UF", "HF", "HF", "HF", "UF", "HF", "NF", "UF", "UF", "HF", "NF", "UF", "UF", "HF", "NF")
brand.type <- factor (brand.type.list, levels= c("UF", "HF", "NF"), labels= c("Unhealthy Food", "Healthy Food","Non-Food"))
rm(brand.type.list)

# Endorsement Type + Presence
brand.endorsement.list <- c("P", "S", "C", "C", "P", "C", "N", "P", "C", "S", "P", "C", "S", "P", "C", "S", "P", "C", "S", "P", "C", "S", "P", "C", "S", "S", "C", "P", "P", "C", "S", "P", "C", "N", "P", "S", "C", "C", "C", "P", "S", "N", "N", "S", "N", "N", "N", "N", "N", "N", "N", "N", "N", "N", "N", "N")
brand.endorsement <- factor(brand.endorsement.list, levels= c("P", "C", "S", "N"), labels= c("Peer", "Celebrity","Sponsored", "Not Present"))
rm(brand.endorsement.list)

interaction <- interaction(brand.type, brand.endorsement)

# Happy to Like
happy.to.like.list.frequencies <- c(sum(data$happy.to.like_1, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_2, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_3, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_4, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_5, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_6, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_7, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_8, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_9, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_10, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_11, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_12, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_13, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_14, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_15, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_16, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_17, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_18, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_19, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_20, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_21, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_22, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_23, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_24, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_25, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_26, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_27, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_28, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_29, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_30, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_31, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_32, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_33, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_34, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_35, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_36, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_37, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_38, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_39, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_40, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_41, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_42, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_43, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_44, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_45, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_46, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_47, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_48, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_49, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_50, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_51, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_52, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_53, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_54, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_55, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_56, na.rm = TRUE))

# Combine into a dataframe
happy.to.like.dataframe <- data.frame(brands, brand.type, brand.endorsement, happy.to.like.list.frequencies, interaction)
```

## Willing to like Products coloured by Type

```{r fig.width=14, fig.height=20, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# Chart it sorted by brands
ggplot(data=happy.to.like.dataframe, aes(x=reorder(brands, happy.to.like.list.frequencies), y= happy.to.like.list.frequencies, fill=brand.type)) +
  geom_bar(stat="identity") +
  scale_y_continuous("Number of Participants willing to like") + 
  xlab("Brands") + 
  scale_fill_discrete(name="Brand type") +
  theme_fivethirtyeight() + scale_fill_gdocs(name="Brand type") +
  theme(text = element_text(size=20)) +
  coord_flip()
```

## Willing to like Products coloured by Endorsement

```{r fig.width=14, fig.height=20, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# Chart it sorted by endorsement
ggplot(data=happy.to.like.dataframe, aes(x=reorder(brands, happy.to.like.list.frequencies), y= happy.to.like.list.frequencies, fill=brand.endorsement)) +
  geom_bar(stat="identity") +
  scale_y_continuous("Number of Participants willing to like") + 
  xlab("Brands") + 
  scale_fill_discrete(name="Endorsement") +
  theme_fivethirtyeight() + scale_fill_gdocs(name="Endorsement type") +
  theme(text = element_text(size=20)) +
  coord_flip()
```

## Willing to like Products coloured by Interaction

```{r fig.width=14, fig.height=20, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# Chart it sorted by endorsement
ggplot(data=happy.to.like.dataframe, aes(x=reorder(brands, happy.to.like.list.frequencies), y= happy.to.like.list.frequencies, fill=interaction)) +
  geom_bar(stat="identity") +
  scale_y_continuous("Number of Participants willing to like") + 
  xlab("Brands") + 
  scale_fill_discrete(name="Endorsement") +
  theme_fivethirtyeight() + scale_fill_gdocs(name="Endorsement type") +
  theme(text = element_text(size=20)) +
  coord_flip()
```



```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

# Note - A number of the brands are unique to gender, so that should be factored in. 
# Maybe dividing by the n of that gender and multiplying by total members?


# Familiarity

# These scores are adjusted by gender
total.male <- sum(data$gender == 1)
total.female <- sum(data$gender == 2)
total.participants <- total.male + total.female

familiarity.frequencies <- c(sum(data$familiarity_1, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_2, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_3, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_4, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_5, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_6, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_7, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_8, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_9, na.rm = TRUE)*total.participants/total.female)
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_10, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_11, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_12, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_13, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_14, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_15, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_16, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_17, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_18, na.rm = TRUE)*total.participants/total.female)
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_19, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_20, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_21, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_22, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_23, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_24, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_25, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_26, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_27, na.rm = TRUE)*total.participants/total.female)
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_28, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_29, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_30, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_31, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_32, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_33, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_34, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_35, na.rm = TRUE)*total.participants/total.female)
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_36, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_37, na.rm = TRUE)*total.participants/total.male)
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_38, na.rm = TRUE)*total.participants/total.male)
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_39, na.rm = TRUE)*total.participants/total.male)
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_40, na.rm = TRUE)*total.participants/total.male)
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_41, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_42, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_43, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_44, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_45, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_46, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_47, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_48, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_49, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_50, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_51, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_52, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_53, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_54, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_55, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_56, na.rm = TRUE))

# Combine into a dataframe
familiarity.dataframe <- data.frame(brands, brand.type, brand.endorsement, familiarity.frequencies, interaction)

# Remove the brands that were not included in the profiles
familiarity.dataframe<-familiarity.dataframe[!(familiarity.dataframe$brand.endorsement=="Not Present"),]

```

## Prompted recall of brands coloured by brand type

```{r fig.width=14, fig.height=20, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# Chart the results
ggplot(data=familiarity.dataframe, aes(x=reorder(brands, familiarity.frequencies), y=familiarity.frequencies, fill=brand.type)) +
  geom_bar(stat="identity") +
  scale_y_continuous("Number of Participants indicating familiarity") + 
  xlab("Brands") + 
  theme_fivethirtyeight() + scale_fill_gdocs(name="Brand type") +
  theme(text = element_text(size=20)) +
  coord_flip()
```

## Prompted recall of brands coloured by endorsement type

```{r fig.width=14, fig.height=20, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# Chart the results showing endorsement
ggplot(data=familiarity.dataframe, aes(x=reorder(brands, familiarity.frequencies), y=familiarity.frequencies, fill=brand.endorsement)) +
  geom_bar(stat="identity") +
  scale_y_continuous("Number of Participants indicating familiarity") + 
  xlab("Brands") + 
  theme_fivethirtyeight() + scale_fill_gdocs(name="Endorsement type") +
  theme(text = element_text(size=20)) +
  coord_flip()

```

## Prompted recall of brands coloured by interaction

```{r fig.width=14, fig.height=20, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# Chart the results showing endorsement
ggplot(data=familiarity.dataframe, aes(x=reorder(brands, familiarity.frequencies), y=familiarity.frequencies, fill=interaction)) +
  geom_bar(stat="identity") +
  scale_y_continuous("Number of Participants indicating familiarity") + 
  xlab("Brands") + 
  theme_fivethirtyeight() + scale_fill_gdocs(name="Endorsement type") +
  theme(text = element_text(size=20)) +
  coord_flip()

```


```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

# Note - A number of the brands are unique to gender, so that should be factored in. 
# Maybe dividing by the n of that gender and multiplying by total members?


# Profile Rating

profile_ratings <- mean(cbind(data$f001a, data$m001a), na.rm = TRUE) # Ben & Jerries
profile_ratings <- c(profile_ratings, mean(cbind(data$f003a, data$m003a), na.rm = TRUE)) # McDonalds
profile_ratings <- c(profile_ratings, mean(cbind(data$f002a, data$m002a), na.rm = TRUE)) # Subway
profile_ratings <- c(profile_ratings, mean(cbind(data$f036a, data$m036a), na.rm = TRUE)) # Luckies Smartphone projector 
profile_ratings <- c(profile_ratings, mean(cbind(data$f004a, data$m004a), na.rm = TRUE)) # Tesco Muesli
profile_ratings <- c(profile_ratings, mean(cbind(data$f005a, data$m005a), na.rm = TRUE)) # Good4U Seeds
profile_ratings <- c(profile_ratings, NA) # Bord Bia 
profile_ratings <- c(profile_ratings, mean(cbind(data$f007a, data$m007a), na.rm = TRUE)) # Jam 
profile_ratings <- c(profile_ratings, mean(data$f008a, na.rm = TRUE)) # F = Dior Poison
profile_ratings <- c(profile_ratings, mean(cbind(data$f009a, data$m009a), na.rm = TRUE)) # Sennheiser headphones
profile_ratings <- c(profile_ratings, mean(cbind(data$f010a, data$m010a), na.rm = TRUE)) # Eddie Rockets
profile_ratings <- c(profile_ratings, mean(cbind(data$f011a, data$m011a), na.rm = TRUE)) # KFC 
profile_ratings <- c(profile_ratings, mean(cbind(data$f012a, data$m012a), na.rm = TRUE)) # Apache Pizza 
profile_ratings <- c(profile_ratings, mean(cbind(data$f013a, data$m013a), na.rm = TRUE)) # Uncle Bens Brown Rice
profile_ratings <- c(profile_ratings, mean(cbind(data$f014a, data$m014a), na.rm = TRUE)) # Danone Yoghurt
profile_ratings <- c(profile_ratings, mean(cbind(data$f015a, data$m015a), na.rm = TRUE)) # Kelkin Rice Cakes
profile_ratings <- c(profile_ratings, mean(cbind(data$f016a, data$m016a), na.rm = TRUE)) # H&M Denim
profile_ratings <- c(profile_ratings, mean(data$f017a, na.rm = TRUE)) # F = Honest Beautys Truly Kissable
profile_ratings <- c(profile_ratings, mean(cbind(data$f018a, data$m018a), na.rm = TRUE)) # Adidas Shoes
profile_ratings <- c(profile_ratings, mean(cbind(data$f019a, data$m019a), na.rm = TRUE)) # Doritos
profile_ratings <- c(profile_ratings, mean(cbind(data$f020a, data$m020a), na.rm = TRUE)) # Coco Pops
profile_ratings <- c(profile_ratings, mean(cbind(data$f021a, data$m021a), na.rm = TRUE)) # Walkers crisps
profile_ratings <- c(profile_ratings, mean(cbind(data$f022a, data$m022a), na.rm = TRUE)) # Weetabix
profile_ratings <- c(profile_ratings, mean(cbind(data$f023a, data$m023a), na.rm = TRUE)) # Fyffes Bananas
profile_ratings <- c(profile_ratings, mean(cbind(data$f024a, data$m024a), na.rm = TRUE)) # Chopped
profile_ratings <- c(profile_ratings, mean(cbind(data$f025a, data$m025a), na.rm = TRUE)) # Penneys 
profile_ratings <- c(profile_ratings, mean(data$f026a, na.rm = TRUE)) # F = Covergirl
profile_ratings <- c(profile_ratings, mean(cbind(data$f027a, data$m027a), na.rm = TRUE)) # ASOS (Star Wars tshirt)
profile_ratings <- c(profile_ratings, mean(cbind(data$f028a, data$m028a), na.rm = TRUE)) # Bunsen burgers
profile_ratings <- c(profile_ratings, mean(cbind(data$f029a, data$m029a), na.rm = TRUE)) # Creme Egg
profile_ratings <- c(profile_ratings, mean(cbind(data$f030a, data$m030a), na.rm = TRUE)) # Supermacs Chicken burger
profile_ratings <- c(profile_ratings, mean(cbind(data$f031a, data$m031a), na.rm = TRUE)) # Special K 
profile_ratings <- c(profile_ratings, mean(cbind(data$f032a, data$m032a), na.rm = TRUE)) # John West Tuna
profile_ratings <- c(profile_ratings, NA) # The foods of athenry
profile_ratings <- c(profile_ratings, mean(data$f034a, na.rm = TRUE)) # F= CB Tan
profile_ratings <- c(profile_ratings, mean(cbind(data$f035a, data$m035a), na.rm = TRUE)) # Nike
profile_ratings <- c(profile_ratings, mean(data$m008a, na.rm = TRUE)) # M = Under armor
profile_ratings <- c(profile_ratings, mean(data$m017a, na.rm = TRUE)) # M = Unchartered 4
profile_ratings <- c(profile_ratings, mean(data$m026a, na.rm = TRUE)) # M = Nerf
profile_ratings <- c(profile_ratings, mean(data$m034a, na.rm = TRUE)) # M = Google Chromecast
profile_ratings <- c(profile_ratings, mean(cbind(data$f033a, data$m033a), na.rm = TRUE)) # Irish Pride Healthy Grain
profile_ratings <- c(profile_ratings, NA) # Burger King
profile_ratings <- c(profile_ratings, NA) # Yoplait
profile_ratings <- c(profile_ratings, mean(cbind(data$f006a, data$m006a), na.rm = TRUE)) # Keelings 
profile_ratings <- c(profile_ratings, NA) # Avonmore
profile_ratings <- c(profile_ratings, NA) # Tayto
profile_ratings <- c(profile_ratings, NA) # Fruit & Fibre
profile_ratings <- c(profile_ratings, NA) # Reebok
profile_ratings <- c(profile_ratings, NA) # Domino's pizza
profile_ratings <- c(profile_ratings, NA) # Hagen Daaz
profile_ratings <- c(profile_ratings, NA) # Ready Brek
profile_ratings <- c(profile_ratings, NA) # Dunnes
profile_ratings <- c(profile_ratings, NA) # Cheetos
profile_ratings <- c(profile_ratings, NA) # Kitkat
profile_ratings <- c(profile_ratings, NA) # Alpen Muesli
profile_ratings <- c(profile_ratings, NA) # Beats

# Combine into a dataframe
profile_ratings_dataframe <- data.frame(brands, brand.type, brand.endorsement, profile_ratings, interaction)

# Remove the brands that were not included in the profiles
profile_ratings_dataframe<-profile_ratings_dataframe[!(profile_ratings_dataframe$brand.endorsement=="Not Present"),]
```

## Mean profile ratings coloured by brand type

```{r fig.width=14, fig.height=20, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# Chart the results
ggplot(data=profile_ratings_dataframe, aes(x=reorder(brands, profile_ratings), y=profile_ratings, fill=brand.type)) +
  geom_bar(stat="identity") +
  scale_y_continuous("Mean Rating by Profile") + 
  xlab("Brands") + 
  theme_fivethirtyeight() + scale_fill_gdocs(name="Brand type") +
  theme(text = element_text(size=20)) +
  coord_flip()
```

## Mean profile ratings coloured by endorsement type

```{r fig.width=14, fig.height=20, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# Chart the results showing endorsement
ggplot(data=profile_ratings_dataframe, aes(x=reorder(brands, profile_ratings), y=profile_ratings, fill=brand.endorsement)) +
  geom_bar(stat="identity") +
  scale_y_continuous("Mean Rating by Profile") + 
  xlab("Brands") + 
  theme_fivethirtyeight() + scale_fill_gdocs(name="Endorsement type") +
  theme(text = element_text(size=20)) +
  coord_flip()

```

## Mean profile ratings coloured by interaction

```{r fig.width=14, fig.height=20, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# Chart the results showing endorsement
ggplot(data=profile_ratings_dataframe, aes(x=reorder(brands, profile_ratings), y=profile_ratings, fill=interaction)) +
  geom_bar(stat="identity") +
  scale_y_continuous("Mean Rating by Profile") + 
  xlab("Brands") + 
  theme_fivethirtyeight() + scale_fill_gdocs(name="Endorsement type") +
  theme(text = element_text(size=20)) +
  coord_flip()

```


```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

# Note - A number of the brands are unique to gender, so that should be factored in. 
# Maybe dividing by the n of that gender and multiplying by total members?


# Profile Rating

profile_ratings <- mean(cbind(data$f001b1, data$m001b1), na.rm = TRUE) # Ben & Jerries
profile_ratings <- c(profile_ratings, mean(cbind(data$f003b1, data$m003b1), na.rm = TRUE)) # McDonalds
profile_ratings <- c(profile_ratings, mean(cbind(data$f002b1, data$m002b1), na.rm = TRUE)) # Subway
profile_ratings <- c(profile_ratings, mean(cbind(data$f036b2, data$m036b2), na.rm = TRUE)) # Luckies Smartphone projector 
profile_ratings <- c(profile_ratings, mean(cbind(data$f004b1, data$m004b1), na.rm = TRUE)) # Tesco Muesli
profile_ratings <- c(profile_ratings, mean(cbind(data$f005b1, data$m005b1), na.rm = TRUE)) # Good4U Seeds
profile_ratings <- c(profile_ratings, NA) # Bord Bia 
profile_ratings <- c(profile_ratings, mean(cbind(data$f007b1, data$m007b1), na.rm = TRUE)) # Jam 
profile_ratings <- c(profile_ratings, mean(data$f008b1, na.rm = TRUE)) # F = Dior Poison
profile_ratings <- c(profile_ratings, mean(cbind(data$f009b1, data$m009b1), na.rm = TRUE)) # Sennheiser headphones
profile_ratings <- c(profile_ratings, mean(cbind(data$f010b1, data$m010b1), na.rm = TRUE)) # Eddie Rockets
profile_ratings <- c(profile_ratings, mean(cbind(data$f011b1, data$m011b1), na.rm = TRUE)) # KFC 
profile_ratings <- c(profile_ratings, mean(cbind(data$f012b1, data$m012b1), na.rm = TRUE)) # Apache Pizza 
profile_ratings <- c(profile_ratings, mean(cbind(data$f013b1, data$m013b1), na.rm = TRUE)) # Uncle Bens Brown Rice
profile_ratings <- c(profile_ratings, mean(cbind(data$f014b1, data$m014b1), na.rm = TRUE)) # Danone Yoghurt
profile_ratings <- c(profile_ratings, mean(cbind(data$f015b1, data$m015b1), na.rm = TRUE)) # Kelkin Rice Cakes
profile_ratings <- c(profile_ratings, mean(cbind(data$f016b1, data$m016b1), na.rm = TRUE)) # H&M Denim
profile_ratings <- c(profile_ratings, mean(data$f017b1, na.rm = TRUE)) # F = Honest Beautys Truly Kissable
profile_ratings <- c(profile_ratings, mean(cbind(data$f018b1, data$m018b1), na.rm = TRUE)) # Adidas Shoes
profile_ratings <- c(profile_ratings, mean(cbind(data$f019b2, data$m019b2), na.rm = TRUE)) # Doritos
profile_ratings <- c(profile_ratings, mean(cbind(data$f020b2, data$m020b2), na.rm = TRUE)) # Coco Pops
profile_ratings <- c(profile_ratings, mean(cbind(data$f021b2, data$m021b2), na.rm = TRUE)) # Walkers crisps
profile_ratings <- c(profile_ratings, mean(cbind(data$f022b2, data$m022b2), na.rm = TRUE)) # Weetabix
profile_ratings <- c(profile_ratings, mean(cbind(data$f023b2, data$m023b2), na.rm = TRUE)) # Fyffes Bananas
profile_ratings <- c(profile_ratings, mean(cbind(data$f024b2, data$m024b2), na.rm = TRUE)) # Chopped
profile_ratings <- c(profile_ratings, mean(cbind(data$f025b2, data$m025b2), na.rm = TRUE)) # Penneys 
profile_ratings <- c(profile_ratings, mean(data$f026b2, na.rm = TRUE)) # F = Covergirl
profile_ratings <- c(profile_ratings, mean(cbind(data$f027b2, data$m027b2), na.rm = TRUE)) # ASOS (Star Wars tshirt)
profile_ratings <- c(profile_ratings, mean(cbind(data$f028b2, data$m028b2), na.rm = TRUE)) # Bunsen burgers
profile_ratings <- c(profile_ratings, mean(cbind(data$f029b2, data$m029b2), na.rm = TRUE)) # Creme Egg
profile_ratings <- c(profile_ratings, mean(cbind(data$f030b2, data$m030b2), na.rm = TRUE)) # Supermacs Chicken burger
profile_ratings <- c(profile_ratings, mean(cbind(data$f031b2, data$m031b2), na.rm = TRUE)) # Special K 
profile_ratings <- c(profile_ratings, mean(cbind(data$f032b2, data$m032b2), na.rm = TRUE)) # John West Tuna
profile_ratings <- c(profile_ratings, NA) # The foods of athenry
profile_ratings <- c(profile_ratings, mean(data$f034b2, na.rm = TRUE)) # F= CB Tan
profile_ratings <- c(profile_ratings, mean(cbind(data$f035b2, data$m035b2), na.rm = TRUE)) # Nike
profile_ratings <- c(profile_ratings, mean(data$m008b1, na.rm = TRUE)) # M = Under armor
profile_ratings <- c(profile_ratings, mean(data$m017b1, na.rm = TRUE)) # M = Unchartered 4
profile_ratings <- c(profile_ratings, mean(data$m026b2, na.rm = TRUE)) # M = Nerf
profile_ratings <- c(profile_ratings, mean(data$m034b2, na.rm = TRUE)) # M = Google Chromecast
profile_ratings <- c(profile_ratings, mean(cbind(data$f033b2, data$m033b2), na.rm = TRUE)) # Irish Pride Healthy Grain
profile_ratings <- c(profile_ratings, NA) # Burger King
profile_ratings <- c(profile_ratings, NA) # Yoplait
profile_ratings <- c(profile_ratings, mean(cbind(data$f006b2, data$m006b2), na.rm = TRUE)) # Keelings 
profile_ratings <- c(profile_ratings, NA) # Avonmore
profile_ratings <- c(profile_ratings, NA) # Tayto
profile_ratings <- c(profile_ratings, NA) # Fruit & Fibre
profile_ratings <- c(profile_ratings, NA) # Reebok
profile_ratings <- c(profile_ratings, NA) # Domino's pizza
profile_ratings <- c(profile_ratings, NA) # Hagen Daaz
profile_ratings <- c(profile_ratings, NA) # Ready Brek
profile_ratings <- c(profile_ratings, NA) # Dunnes
profile_ratings <- c(profile_ratings, NA) # Cheetos
profile_ratings <- c(profile_ratings, NA) # Kitkat
profile_ratings <- c(profile_ratings, NA) # Alpen Muesli
profile_ratings <- c(profile_ratings, NA) # Beats

# Combine into a dataframe
profile_ratings_dataframe <- data.frame(brands, brand.type, brand.endorsement, profile_ratings, interaction)

# Remove the brands that were not included in the profiles
profile_ratings_dataframe<-profile_ratings_dataframe[!(profile_ratings_dataframe$brand.endorsement=="Not Present"),]
```

## Mean post ratings coloured by brand type

```{r fig.width=14, fig.height=20, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# Chart the results
ggplot(data=profile_ratings_dataframe, aes(x=reorder(brands, profile_ratings), y=profile_ratings, fill=brand.type)) +
  geom_bar(stat="identity") +
  scale_y_continuous("Mean Rating by Profile") + 
  xlab("Brands") + 
  theme_fivethirtyeight() + scale_fill_gdocs(name="Brand type") +
  theme(text = element_text(size=20)) +
  coord_flip()
```

## Mean post ratings coloured by endorsement type

```{r fig.width=14, fig.height=20, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# Chart the results showing endorsement
ggplot(data=profile_ratings_dataframe, aes(x=reorder(brands, profile_ratings), y=profile_ratings, fill=brand.endorsement)) +
  geom_bar(stat="identity") +
  scale_y_continuous("Mean Rating by Profile") + 
  xlab("Brands") + 
  theme_fivethirtyeight() + scale_fill_gdocs(name="Endorsement type") +
  theme(text = element_text(size=20)) +
  coord_flip()
```

## Mean post ratings coloured by interaction

```{r fig.width=14, fig.height=20, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# Chart the results showing endorsement
ggplot(data=profile_ratings_dataframe, aes(x=reorder(brands, profile_ratings), y=profile_ratings, fill=interaction)) +
  geom_bar(stat="identity") +
  scale_y_continuous("Mean Rating by Profile") + 
  xlab("Brands") + 
  theme_fivethirtyeight() + scale_fill_gdocs(name="Endorsement type") +
  theme(text = element_text(size=20)) +
  coord_flip()
```


