---
title: "Product Analysis"
author: "Barry Sheppard"
date: "20 June 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a breakdown of results based on products rather than factors. As there are a number of products which are only displayed to one gender, these results were adjusted to give a proportional value (i.e. values were divided by total number of participants in that gender and multiplied by the total number of participants).

```{r products, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

# Set working director
setwd("~/GitHub/KidsFoodandFacebook")

# Import Libraries required

# install.packages("magrittr")
library("magrittr")
# install.packages("tidyr")
library("tidyr")
# install.packages("ggplot2")
library("ggplot2")
# install.packages("cowplot")
library("cowplot")
# install.packages("plyr")
library("plyr")
# install.packages("psych)
library("psych")

library(ggthemes)

# Load the data
source("load.R", print.eval=TRUE)

# Familiarity totals

# Brand list
brands <- c("Ben & Jerries", "McDonalds", "Subway", "Luckies", "Tesco", "Good4U", "Bord Bia", "Jam", "Dior", "Sennheiser", "Eddie Rockets")
brands <- c(brands, "KFC", "Apache Pizza", "Uncle Bens Rice", "Danone", "Kelkin", "H&M", "Truly Kissable", "Adidas", "Doritos", "Coco pops")
brands <- c(brands, "Walkers", "Weetabix", "Fyffes", "Chopped", "Penneys", "Covergirl", "ASOS", "Bunsen", "Creme Egg", "Supermacs", "Special K")
brands <- c(brands, "John West", "The Foods of Athenry", "CB tanning", "Nike", "Under armor", "Uncharted 4", "Nerf", "Google", "Irish Pride")
brands <- c(brands, "Burger King", "Yoplait", "Keelings", "Avonmore", "Tayto", "Fruit & Fibre", "Reebok", "Domino's Pizza", "Hagen Daaz", "Ready Brek")
brands <- c(brands, "Dunnes", "Cheetos", "Kitkat", "Alpen Muesli", "Beats")

# Brand Type
brand.type.list <- c("UF", "UF", "UF", "NF", "HF", "HF", "HF", "NF", "NF", "NF", "UF", "UF", "UF", "HF", "HF", "HF", "NF", "NF", "NF", "UF", "UF", "UF", "HF", "HF", "HF", "NF", "NF", "NF", "UF", "UF", "UF", "HF", "HF", "HF", "NF", "NF", "NF", "NF", "NF", "NF", "HF", "UF", "HF", "HF", "HF", "UF", "HF", "NF", "UF", "UF", "HF", "NF", "UF", "UF", "HF", "NF")
brand.type <- factor (brand.type.list, levels= c("UF", "HF", "NF"), labels= c("Unhealthy Food", "Healthy Food","Non-Food"))
rm(brand.type.list)

# Endorsement Type + Presence
brand.endorsement.list <- c("P", "S", "C", "C", "P", "C", "N", "P", "C", "S", "P", "C", "S", "P", "C", "S", "P", "C", "S", "P", "C", "S", "P", "C", "S", "S", "C", "P", "P", "C", "S", "P", "C", "N", "P", "S", "C", "C", "C", "P", "S", "N", "N", "S", "N", "N", "N", "N", "N", "N", "N", "N", "N", "N", "N", "N")
brand.endorsement <- factor(brand.endorsement.list, levels= c("P", "C", "S", "N"), labels= c("Peer", "Celebrity","Sponsored", "Not Present"))
rm(brand.endorsement.list)

# Happy to Like
happy.to.like.list.frequencies <- c(sum(data$happy.to.like_1, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_2, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_3, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_4, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_5, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_6, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_7, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_8, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_9, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_10, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_11, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_12, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_13, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_14, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_15, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_16, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_17, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_18, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_19, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_20, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_21, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_22, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_23, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_24, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_25, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_26, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_27, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_28, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_29, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_30, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_31, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_32, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_33, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_34, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_35, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_36, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_37, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_38, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_39, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_40, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_41, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_42, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_43, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_44, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_45, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_46, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_47, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_48, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_49, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_50, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_51, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_52, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_53, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_54, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_55, na.rm = TRUE))
happy.to.like.list.frequencies <- c(happy.to.like.list.frequencies, sum(data$happy.to.like_56, na.rm = TRUE))

# Combine into a dataframe
happy.to.like.dataframe <- data.frame(brands, brand.type, brand.endorsement, happy.to.like.list.frequencies)
```

## Willing to like Products by Type

```{r fig.width=14, fig.height=20, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# Chart it sorted by brands
ggplot(data=happy.to.like.dataframe, aes(x=reorder(brands, happy.to.like.list.frequencies), y= happy.to.like.list.frequencies, fill=brand.type)) +
  geom_bar(stat="identity") +
  scale_y_continuous("Number of Participants willing to like") + 
  xlab("Brands") + 
  scale_fill_discrete(name="Brand type") +
  theme_fivethirtyeight() + scale_fill_gdocs(name="Brand type") +
  theme(text = element_text(size=20)) +
  coord_flip()
```

## Willing to like Products by Endorsement

```{r fig.width=14, fig.height=20, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# Chart it sorted by endorsement
ggplot(data=happy.to.like.dataframe, aes(x=reorder(brands, happy.to.like.list.frequencies), y= happy.to.like.list.frequencies, fill=brand.endorsement)) +
  geom_bar(stat="identity") +
  scale_y_continuous("Number of Participants willing to like") + 
  xlab("Brands") + 
  scale_fill_discrete(name="Endorsement") +
  theme_fivethirtyeight() + scale_fill_gdocs(name="Endorsement type") +
  theme(text = element_text(size=20)) +
  coord_flip()
```



```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

# Note - A number of the brands are unique to gender, so that should be factored in. 
# Maybe dividing by the n of that gender and multiplying by total members?


# Familiarity

# These scores are adjusted by gender
total.male <- sum(data$gender == 1)
total.female <- sum(data$gender == 2)
total.participants <- total.male + total.female

familiarity.frequencies <- c(sum(data$familiarity_1, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_2, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_3, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_4, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_5, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_6, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_7, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_8, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_9, na.rm = TRUE)*total.participants/total.female)
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_10, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_11, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_12, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_13, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_14, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_15, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_16, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_17, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_18, na.rm = TRUE)*total.participants/total.female)
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_19, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_20, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_21, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_22, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_23, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_24, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_25, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_26, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_27, na.rm = TRUE)*total.participants/total.female)
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_28, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_29, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_30, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_31, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_32, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_33, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_34, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_35, na.rm = TRUE)*total.participants/total.female)
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_36, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_37, na.rm = TRUE)*total.participants/total.male)
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_38, na.rm = TRUE)*total.participants/total.male)
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_39, na.rm = TRUE)*total.participants/total.male)
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_40, na.rm = TRUE)*total.participants/total.male)
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_41, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_42, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_43, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_44, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_45, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_46, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_47, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_48, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_49, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_50, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_51, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_52, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_53, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_54, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_55, na.rm = TRUE))
familiarity.frequencies <- c(familiarity.frequencies, sum(data$familiarity_56, na.rm = TRUE))

# Combine into a dataframe
familiarity.dataframe <- data.frame(brands, brand.type, brand.endorsement, familiarity.frequencies)

# Remove the brands that were not included in the profiles
familiarity.dataframe<-familiarity.dataframe[!(familiarity.dataframe$brand.endorsement=="Not Present"),]

```

## Prompted recall of brands by brand type

```{r fig.width=14, fig.height=20, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# Chart the results
ggplot(data=familiarity.dataframe, aes(x=reorder(brands, familiarity.frequencies), y=familiarity.frequencies, fill=brand.type)) +
  geom_bar(stat="identity") +
  scale_y_continuous("Number of Participants indicating familiarity") + 
  xlab("Brands") + 
  theme_fivethirtyeight() + scale_fill_gdocs(name="Brand type") +
  theme(text = element_text(size=20)) +
  coord_flip()
```

## Prompted recall of brands by endorsement type

```{r fig.width=14, fig.height=20, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# Chart the results showing endorsement
ggplot(data=familiarity.dataframe, aes(x=reorder(brands, familiarity.frequencies), y=familiarity.frequencies, fill=brand.endorsement)) +
  geom_bar(stat="identity") +
  scale_y_continuous("Number of Participants indicating familiarity") + 
  xlab("Brands") + 
  theme_fivethirtyeight() + scale_fill_gdocs(name="Endorsement type") +
  theme(text = element_text(size=20)) +
  coord_flip()

```

