---
title: "Prompted Recall"
author: "Barry Sheppard"
date: "16 June 2016"
output: html_document
---



```{r load, include=FALSE}
# Loading up some data
library(plyr)
library(dplyr)
library(tidyr)
library(psych)
library(BayesFactor)
library(MASS)
library(vcd)
library(vcdExtra)
library(gmodels)

source("load.R", print.eval=TRUE)

# Rename for the graph
prompted_recall <- plyr::rename(prompted_recall, c("recall"="Recall", "product"="Product", "endorse"="Endorsement"))

# Table for prompted Recall
prompted_recall_table <- xtabs(~Product + Endorsement + Recall, data=prompted_recall)

```

## Analysis

### Responses

```{r, echo=FALSE}
# count the total responses per person (only valid responses)
print(c("Mean of responses", round(mean(data$total_fam[fam_true]), 2)))
print(c("Standard deviation of responses", round(sd(data$total_fam[fam_true]),2)))

# Count of correct data
print(c("Mean of correct responses", round(mean(rating$count),2)))
print(c("Standard deviation of correct responses", round(sd(rating$count),2)))
```

## 2x2 Breakdowns - Products

### Product: Healthy vs Unhealthy

```{r, echo=FALSE, error=FALSE}
# Subset the data to remove NonFood so we can compare Unhealthy and Healthy 
data_subset <- subset(prompted_recall, Product!="NonFood")
# Refactor Product to remove the unused factor
data_subset$Product <- factor(data_subset$Product)
# Prepare the data
prompted_recall_table_1 <- xtabs(~ Product + Recall, data_subset)
# Show the data + results
CrossTable(prompted_recall_table_1, chisq = TRUE, expected = TRUE, asresid = TRUE, format = "SPSS", digits = 2)

# Bayes Factors - indepMultinomial, generalised form
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))

# This is a Log Linear model and displayed as a mosaic, a little excessive as we're only displaying the table
model_joint_indep <- loglm(formula = ~ Product + Recall, data=prompted_recall_table_1)
plot(model_joint_indep, panel = mosaic, type = "observed", pop=FALSE, shade=FALSE, legend=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)

```

### Product: Nonfood vs Unhealthy

```{r, echo=FALSE}

# Subset the data to remove NonFood so we can compare Unhealthy and Nonfood
data_subset <- subset(prompted_recall, Product!="Healthy")
# Refactor Product to remove the unused factor
data_subset$Product <- factor(data_subset$Product)
# Prepare the data
prompted_recall_table_1 <- xtabs(~Product + Recall, data_subset)
# Show the data + results
CrossTable(prompted_recall_table_1, chisq = TRUE, expected = TRUE, asresid = TRUE, format = "SPSS", digits = 2)
# Bayes Factors
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))
# This is a Log Linear model and displayed as a mosaic, a little excessive as we're only displaying the table
model_joint_indep <- loglm(formula = ~ Product + Recall, data=prompted_recall_table_1)
plot(model_joint_indep, panel = mosaic, type = "observed", pop=FALSE, shade=FALSE, legend=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)
```

### Product: Healthy vs Nonfood

```{r, echo=FALSE}
# Subset the data to remove NonFood so we can compare Healthy and Nonfood
data_subset <- subset(prompted_recall, Product!="Unhealthy")
# Refactor Product to remove the unused factor
data_subset$Product <- factor(data_subset$Product)
# Prepare the data
prompted_recall_table_1 <- xtabs(~Product + Recall, data_subset)
# Show the data + Results
CrossTable(prompted_recall_table_1, chisq = TRUE, expected = TRUE, asresid = TRUE, format = "SPSS", digits = 2)
# Bayes Factors
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))
# This is a Log Linear model and displayed as a mosaic, a little excessive as we're only displaying the table
model_joint_indep <- loglm(formula = ~ Product + Recall, data=prompted_recall_table_1)
plot(model_joint_indep, panel = mosaic, type = "observed", pop=FALSE, shade=FALSE, legend=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)
```


## 2x2 Breakdowns - Endorsement

### Endorsement: Peer vs Celebrity

```{r, echo=FALSE}
# Subset the data to remove Sponsored so we can compare Peer and Celebrity 
data_subset <- subset(prompted_recall, Endorsement!="Sponsored")
# Refactor Endorsement to remove the unused factor
data_subset$Endorsement <- factor(data_subset$Endorsement)
# Prepare the data
prompted_recall_table_1 <- xtabs(~Endorsement + Recall, data_subset)
# Show the data + results
CrossTable(prompted_recall_table_1, chisq = TRUE, expected = TRUE, asresid = TRUE, format = "SPSS", digits = 2)
# Bayes Factors
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))
# This is a Log Linear model and displayed as a mosaic, a little excessive as we're only displaying the table
model_joint_indep <- loglm(formula = ~ Endorsement + Recall, data=prompted_recall_table_1)
plot(model_joint_indep, panel = mosaic, type = "observed", pop=FALSE, shade=FALSE, legend=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)
```

### Endorsement: Peer vs Sponsored

```{r, echo=FALSE}

# Subset the data to remove Celebrity so we can compare Peer and Sponsored 
data_subset <- subset(prompted_recall, Endorsement!="Celebrity")
# Refactor Endorsement to remove the unused factor
data_subset$Endorsement <- factor(data_subset$Endorsement)
# Prepare the data
prompted_recall_table_1 <- xtabs(~Endorsement + Recall, data_subset)
# Show the data + results
CrossTable(prompted_recall_table_1, chisq = TRUE, expected = TRUE, asresid = TRUE, format = "SPSS", digits = 2)
# Bayes Factors
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))
# This is a Log Linear model and displayed as a mosaic, a little excessive as we're only displaying the table
model_joint_indep <- loglm(formula = ~ Endorsement + Recall, data=prompted_recall_table_1)
plot(model_joint_indep, panel = mosaic, type = "observed", pop=FALSE, shade=FALSE, legend=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)
```

### Endorsement: Celebrity vs Sponsored

```{r, echo=FALSE}

# Subset the data to remove Peer so we can compare Celebrity and Sponsored
data_subset <- subset(prompted_recall, Endorsement!="Peer")
# Refactor Endorsement to remove the unused factor
data_subset$Endorsement <- factor(data_subset$Endorsement)
# Prepare the data
prompted_recall_table_1 <- xtabs(~Endorsement + Recall, data_subset)
# Show the data + results
CrossTable(prompted_recall_table_1, chisq = TRUE, expected = TRUE, asresid = TRUE, format = "SPSS", digits = 2)
# Bayes Factors
BF <- contingencyTableBF(prompted_recall_table_1, sampleType = "indepMulti", fixedMargin = "rows")
BF
print(c("BF10:", format(exp(BF@bayesFactor$bf), scientific=FALSE)))
# This is a Log Linear model and displayed as a mosaic, a little excessive as we're only displaying the table
model_joint_indep <- loglm(formula = ~ Endorsement + Recall, data=prompted_recall_table_1)
plot(model_joint_indep, panel = mosaic, type = "observed", pop=FALSE, shade=FALSE, legend=FALSE)
labeling_cells(text = prompted_recall_table_1, margin = 0)(prompted_recall_table_1)
```


## Analysis

Full interaction of Product * endorsement * Recall

```{r describe, echo=FALSE, messages=FALSE, warning=FALSE}

# Table the prompted Recall table
ftable(prompted_recall_table)
table <- ftable(prompted_recall_table)
print("Percentages")
round(prop.table(table, 1),2)

# Xtabs for the prompoted Recall
P1 <- summary(prompted_recall_table)
P1
print(c("P = ", format(P1$p.value, scientific=FALSE)))

BF1 <- contingencyTableBF(prompted_recall_table, sampleType = "indepMulti", fixedMargin = "rows")
BF1
print(c("BF10:", format(exp(BF1@bayesFactor$bf), scientific=FALSE)))

```



# The Log Linear Analysis

```{r}

# Table for prompted Recall
prompted_recall_table <- xtabs(~ Product + Endorsement + Recall, data=prompted_recall)

# Saturated model
saturated <- loglm(~ Endorsement * Product * Recall, data=prompted_recall_table)
summary(saturated)
# Three way interaction
threeway <- loglm(~ Endorsement + Product + Recall + Endorsement:Product + Endorsement:Recall + Product:Recall, data=prompted_recall_table)
summary(threeway)
# Compare the models
anova(threeway, saturated)


```


To determine which areas to focus on for the difference we need to look at the residuals





```{r}



```


